The journey of Multiple Sequence Alignment

### 2021-08-05 MSA_Notum_journey.Rmd
add sequences from the results of tblastn Hs|WIF1 vs sponges

>>>>

# Search four "representative" proteins that have the WIF domain respect to sponges
In the tree of WIF from oma.db we can see 4 big clusters that have particular characteristics
One is the cluster of the Human WIF (HS|WIF1) the the human with RYK domain (Hs|RYK) then those with 
NTR domain and then those with the "pure"  PK_TYR_SER_THR_PKinase
We will tblastn from each cluster one and evaluate some of the results
## The selected sequences:

### Hs|WIF1 
```{bash}
>Hs|WIF1 gi|111125011|ref|NP_009122.2| gi|111125011|ref|NP_009122.2| wnt inhibitory factor 1 precursor [Homo sapiens]
MARRSAFPAAALWLWSILLCLLALRAEAGPPQEESLYLWIDAHQARVLIGFEEDILIVSEGKMAPFTHDFRKAQQRMPAI
PVNIHSMNFTWQAAGQAEYFYEFLSLRSLDKGIMADPTVNVPLLGTVPHKASVVQVGFPCLGKQDGVAAFEVDVIVMNSE
GNTILQTPQNAIFFKTCQQAECPGGCRNGGFCNERRICECPDGFHGPHCEKALCTPRCMNGGLCVTPGFCICPPGFYGVN
CDKANCSTTCFNGGTCFYPGKCICPPGLEGEQCEISKCPQPCRNGGKCIGKSKCKCSKGYQGDLCSKPVCEPGCGAHGTC
HEPNKCQCQEGWHGRHCNKRYEASLIHALRPAGAQLRQHTPSLKKAEERRDPPESNYIW
```

### Hs|RYK (picle Rick)
```{bash}
>Hs|RYK gi|54607020|ref|NP_001005861.1| gi|54607020|ref|NP_001005861.1| tyrosine-protein kinase RYK isoform 1 precursor [Homo sapiens]
MRGAARLGRPGRSCLPGARGLRAPPPPPLLLLLALLPLLPAPGAAAAPAPRPPELQSASAGPSVSLYLSEDEVRRLIGLD
AELYYVRNDLISHYALSFSLLVPSETNFLHFTWHAKSKVEYKLGFQVDNVLAMDMPQVNISVQGEVPRTLSVFRVELSCT
GKVDSEVMILMQLNLTVNSSKNFTVLNFKRRKMCYKKLEEVKTSALDKNTSRTIYDPVHAAPTTSTRVFYISVGVCCAVI
FLVAIILAVLHLHSMKRIELDDSISASSSSQGLSQPSTQTTQYLRADTPNNATPITSSLGYPTLRIEKNDLRSVTLLEAK
GKVKDIAISRERITLKDVLQEGTFGRIFHGILIDEKDPNKEKQAFVKTVKDQASEIQVTMMLTESCKLRGLHHRNLLPIT
HVCIEEGEKPMVILPYMNWGNLKLFLRQCKLVEANNPQAISQQDLVHMAIQIACGMSYLARREVIHKDLAARNCVIDDTL
QVKITDNALSRDLFPMDYHCLGDNENRPVRWMALESLVNNEFSSASDVWAFGVTLWELMTLGQTPYVDIDPFEMAAYLKD
GYRIAQPINCPDELFAVMACCWALDPEERPKFQQLVQCLTEFHAALGAYV
```

### Of|1176102141
```{bash}
>Of|1176102141 XP_020621816.1| uncharacterized protein LOC110059462 [Orbicella faveolata]
MAGLEARNFLKVLFLMSVPVLGKCSTKLNVFLDAREVSRFLYDLNTNLFLVQDGVVAPILKTPILSSMIPPIEPYIKDLK
FKFNATGMVQYSLNFKSSNETIMKHPTANIRLNGLVPRKTKVFRVKFPCTGKVIGGVLLTINISFVDVAGSEIWGPLSLT
LKRQCVSGNDDLINRYNSTESGEVSPLPAPQICNKRCSKRHVMRRFCLSDFVIKARMESEVMRNGLPRLRLRIARTYKQG
KVKINNKNQLMEKRGQEITCSCSNLKVNKVYLILGKEDKRKRVLFLDNFSTALEWNKNGKSYVKTFRNRSSCPERKMP
```

### Ci|198430807
```{bash}
>Ci|198430807 ref|XP_002129769.1| PREDICTED: tyrosine-protein kinase RYK [Ciona intestinalis]
MRVCAYILAVVLLPCMSKCSIDLYLAEDQVEKLFGIADAEMYYIRNGIINENAVNFVAHVQPEHTDLTYLWKVTNKAITV
AYDLDILDVQKSPAQLNTGSVEMNKHSILYPPKLESKSGTIRYSEDLQPQTLKVSLVCTGEREGNVTVTMKLKLVMDSGT
DLVVNIKRLKKCLKTHSFVEDKPVLTDQPSEPNDQDLNLGGTQQSTSAFYISVSVVSSFIVLIVVGVTLWHVRMSKRYQR
SGVDNCIPMQPGAQHLNQFLRPDLPNNALKPPSHSSLMQIITPLINDLGTDINEIQSKLSAIAIPRENVDIGELTLKGTF
ARIYKGTLDDGTPVLIKTVSDMATEEQKRLLLFESSLLRGMHHRNLLSMKHVVLQDDSTPPMVLFHFMEGGNLKHYLQGL
KLKESPGLVSGIFGSGSTKYEQVSTQDLVEMAIQIACGMTYLSKRGLVHKDLAARNCVIDRDLKVKISDNALSRDAFPAD
YCCLGDNENRPVRWLGLESLVHKVYSSASDVWSFGVLLWELQSLAATPYADIDDFEMASYLKDGFRLSQPINCPDHLYSI
IASCWHYSPDQRPSFTKLLQMLTEFYAELEVYV
```
## Results:
### Hs|WIF1 vs Halisarca caerulea comp25790_c0_seq1 transcribed RNA sequence
```{bash}
>Hc|comp25790
CQRAECIPGCLNGGTCAGPNWCRCARGWSGNRCRRAVCIPACNNGGKCTAPNTCECAEGWTGNQCQRPVCDSECLNGGIC
AAPNTCQCSSGWSGDHCDLPVCRPKCTNGGICIRPSKCLCDSSWTGKRCQKPVCRPGCENGGTCTEPNTCQCTSGWSGDR
C
```
### Hs|WIF1 vs Halichondria panicea TRINITY_DN792_c2_g1_i4, transcribed RNA sequence
```{bash}
>Hp|TRINITY_DN792_c2_g1_i4
CENGGICTQERTCHCAPGYEGPLCEEAVCFPPCTNGGNCTAPGFCECPREWEGIRCEDPGCSPSCENGGTCIRPGECYCT
PQWTGDNCQDAICNPPCGNGGHCISPGHCECGGTGFLGSRCTEAVCKPACENGGECVEPNVCQCLSLWTGNYCDT
```
### Hs|WIF1 vs Aplysina aerophoba TR173969_c0_g2_i1 transcribed RNA sequence
```{bash}
>Ae|TR173969_c0_g2_i1
RRCRKAICNEPCRNGGTCTAPNVCACADGYMGQLCEVPVCSRECQNGGICIGKDECQCEMGYSGLHCESAICTDSCMNGG
TCVEPETCTCPANYTGRVCSEPVCIRPCLNVGQCTGPGVCTCTAEFTGDLCEVPICLDPCLNGGYCSAPNVCTCEDGYEG
HNC
```
### Hs|WIF1 vs Leucetta chagosensis breed sponge isolate calcarea TRINITY_DN9568_c1_g1_i1, transcribed RNA sequence
```{bash}
>Lc|TRINITY_DN9568_c1_g1_i1
PKSAWTGSRCQTPVCLPSCQNGGQCVSPQTCSCAAGYTGSSCGNAVCSTSCKNGGSCVSPNKCSCPAGYTGSYCEKAVCS
TSCRNGGSCVRPNTCSCPAGYTGSYCEKAVCSTSCQNGGSCVRPNTCSCPAGYTGSYCEKAVCSTSCKNGGSCVSPNTCS
CPAGYTGSYCEK
```

hmmscan --cut_ga --domtblout my_data/hmm_search/WIF_profile_HS_WIF1vssponges_domtbl.out my_data/pfam/Pfam-A.hmm my_data/Hs_WIF1vs_sponges.fasta > /dev/null
```

## Import hmmscan of WIF1 vs sponges results into R
```{r}
second_line_fields <- c("target_name", "accession_1", "tlen", "query_name",
                        "accession_2", "qlen",   "E-value_full_seq", "score_full_seq",
                        "bias_full_seq",
                        "this_domain_#",  "of_this_domain",  "c-Evalue_this_domain",
                        "i-Evalue_this_domain",  "score_this_domain", "bias_this_domain", 
                        "from_hmm_coord", "to_hmm_coord", "from_ali_coord", "to_ali_coord", 
                        "from_env_coord", "to_env_coord", "acc", "description_of_target_1",
                        "description_of_target_2","description_of_target_3")

WIF_hmmscan <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_profile_HS_WIF1vssponges_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=29;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
